Locally Conservative Discontinuous Petrov-Galerkin Finite Elements for Fluid Problems

### 2013-02-28 docs/Truman/LocalConservation/paper.tex
Added inner layer and discontinuous source results.

@@

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graph4nc.png}
\includegraphics[width=\textwidth]{figs/Hemker/graph4nc_mesh.png}
\caption{Nonconservative with graph norm}
\label{fig:hemkerGraph14nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robust4nc.png}
\includegraphics[width=\textwidth]{figs/Hemker/robust4nc_mesh.png}
\caption{Nonconservative with robust norm}
\label{fig:hemkerRobust14nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graph4c.png}
\includegraphics[width=\textwidth]{figs/Hemker/graph4c_mesh.png}
\caption{Conservative with graph norm}
\label{fig:hemkerGraph14c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robust4c.png}
\includegraphics[width=\textwidth]{figs/Hemker/robust4c_mesh.png}
\caption{Conservative with robust norm}
\label{fig:hemkerRobust14c}
\end{subfigure}
\caption{Hemker problem after 4 refinements}
\label{fig:hemker4}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graph8nc.png}
\includegraphics[width=\textwidth]{figs/Hemker/graph8nc_mesh.png}
\caption{Nonconservative with graph norm}
\label{fig:hemkerGraph18nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robust8nc.png}
\includegraphics[width=\textwidth]{figs/Hemker/robust8nc_mesh.png}
\caption{Nonconservative with robust norm}
\label{fig:hemkerRobust18nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graph8c.png}
\includegraphics[width=\textwidth]{figs/Hemker/graph8c_mesh.png}
\caption{Conservative with graph norm}
\label{fig:hemkerGraph18c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robust8c.png}
\includegraphics[width=\textwidth]{figs/Hemker/robust8c_mesh.png}
\caption{Conservative with robust norm}
\label{fig:hemkerRobust18c}
\end{subfigure}
\caption{Hemker problem after 8 refinements}
\label{fig:hemker8}
\end{figure}

>>>>

\subsection{Inner Layer Problem}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/InnerLayer/graph8nc.png}
\includegraphics[width=\textwidth]{figs/InnerLayer/graph8nc_mesh.png}
\caption{Nonconservative with graph norm}
\label{fig:innerlayerGraph18nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/InnerLayer/robust8nc.png}
\includegraphics[width=\textwidth]{figs/InnerLayer/robust8nc_mesh.png}
\caption{Nonconservative with robust norm}
\label{fig:innerlayerRobust18nc}
\end{subfigure}
\caption{Inner layer problem after 8 refinements}
\label{fig:innerlayer8nc}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/InnerLayer/graph8c.png}
\includegraphics[width=\textwidth]{figs/InnerLayer/graph8c_mesh.png}
\caption{Conservative with graph norm}
\label{fig:innerlayerGraph18c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/InnerLayer/robust8c.png}
\includegraphics[width=\textwidth]{figs/InnerLayer/robust8c_mesh.png}
\caption{Conservative with robust norm}
\label{fig:innerlayerRobust18c}
\end{subfigure}
\caption{Inner layer problem after 8 refinements}
\label{fig:innerlayer8c}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/InnerLayer/graphFlux.pdf}
\caption{With graph norm}
\label{fig:innerlayerGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/InnerLayer/robustFlux.pdf}
\caption{With robust norm}
\label{fig:innerlayerRobustFlux}
\end{subfigure}
\caption{Flux imbalance in inner layer solutions}
\label{fig:innerlayer_flux}
\end{figure}

\subsection{Discontinuous Source Problem}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Discontinuous/graph8nc.png}
\caption{Nonconservative with graph norm}
\label{fig:discontinuousGraph8nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Discontinuous/robust8nc.png}
\caption{Nonconservative with robust norm}
\label{fig:discontinuousRobust8nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Discontinuous/graph8c.png}
\caption{Conservative with graph norm}
\label{fig:discontinuousGraph8c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Discontinuous/robust8c.png}
\caption{Conservative with robust norm}
\label{fig:discontinuousRobust8c}
\end{subfigure}
\caption{Discontinuous source problem after 8 refinements}
\label{fig:discontinuous}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graphFlux.pdf}
\caption{With graph norm}
\label{fig:discontinuousGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robustFlux.pdf}
\caption{With robust norm}
\label{fig:discontinuousRobustFlux}
\end{subfigure}
\caption{Flux imbalance in discontinuous source solutions}
\label{fig:discontinuous_flux}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graph4nc.png}
\includegraphics[width=\textwidth]{figs/Hemker/graph4nc_mesh.png}
\caption{Nonconservative with graph norm}
\label{fig:hemkerGraph4nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robust4nc.png}
\includegraphics[width=\textwidth]{figs/Hemker/robust4nc_mesh.png}
\caption{Nonconservative with robust norm}
\label{fig:hemkerRobust4nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graph4c.png}
\includegraphics[width=\textwidth]{figs/Hemker/graph4c_mesh.png}
\caption{Conservative with graph norm}
\label{fig:hemkerGraph4c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robust4c.png}
\includegraphics[width=\textwidth]{figs/Hemker/robust4c_mesh.png}
\caption{Conservative with robust norm}
\label{fig:hemkerRobust4c}
\end{subfigure}
\caption{Hemker problem after 4 refinements}
\label{fig:hemker4}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graph8nc.png}
\includegraphics[width=\textwidth]{figs/Hemker/graph8nc_mesh.png}
\caption{Nonconservative with graph norm}
\label{fig:hemkerGraph8nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robust8nc.png}
\includegraphics[width=\textwidth]{figs/Hemker/robust8nc_mesh.png}
\caption{Nonconservative with robust norm}
\label{fig:hemkerRobust8nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graph8c.png}
\includegraphics[width=\textwidth]{figs/Hemker/graph8c_mesh.png}
\caption{Conservative with graph norm}
\label{fig:hemkerGraph8c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robust8c.png}
\includegraphics[width=\textwidth]{figs/Hemker/robust8c_mesh.png}
\caption{Conservative with robust norm}
\label{fig:hemkerRobust8c}
\end{subfigure}
\caption{Hemker problem after 8 refinements}
\label{fig:hemker8}
\end{figure}
